### 2022-05-02 src/text/3-applications-subsections/multi-instrument-analysis.tex
fixed wrong reference to figure
Reformat text files

\begin{figure*}[t]
	\sidecaption
	\includegraphics[width=0.666\textwidth]{figures/multi_instrument_analysis.pdf}
	\caption{A multi-instrument analysis of the Crab Nebula}
	\label{fig:multi_instrument_analysismulti_instrument_analysis}
\end{figure*}

@@

In this multi-instrument analysis example we showcase the capabilities of \gammapy
to perform a simultaneous likelihood fit incorporating data from different instruments
and at different levels of reduction.
We estimate the spectrum of the Crab Nebula combining data from \fermi, \magic and \hawc.
Maps of \fermi data are prepared selecting a region of $X^{\circ}$ around the
position of the Crab Nebula applying the same selection criteria of the 3FHL
catalog (7 years of data with energy from $10\,{\rm GeV}$ to $2\,{\rm TeV}$, \citealt{3FHL}).
%% shall we explain exactly which type of Map is created?
The \magic data are two observations of $20\,{\rm min}$ each, chosen from the
dataset used to estimate the performance of the upgraded stereo system \citep{magic_performance}
and already included in \cite{joint_crab}. The observations were taken at small
zenith angles ($<30^{\circ}$) in wobble mode \citep{fomin_1994}, with the source
sitting at an offset of $0.4^{\circ}$ from the FoV center. Their energy range spans
$80\,{\rm GeV} -- 20\,{\rm TeV}$. They are reduced to ON/OFF dataset before being fitted.
\hawc flux points data are estimated in \cite{hawc_crab_2019} with $2.5\,{\rm years}$
of data and span an energy range $300\,{\rm GeV} -- 300\,{\rm TeV}$, and directly read with \gammapy.

@@

The result of the joint fit is displayed in Fig.~\ref{multi_instrument_analysis}.
We remark that the objective of this exercise is illustrative, we display the
flexibility of \gammapy in simultaneously fitting multi-isntrument data even at
different levels of reduction, we do not aim to provide a new measurement of the
Crab Nebula spectrum.

>>>>

\begin{figure*}[t]
	\sidecaption
	\includegraphics[width=0.666\textwidth]{figures/multi_instrument_analysis.pdf}
	\caption{A multi-instrument analysis of the Crab Nebula}
	\label{fig:multi_instrument_analysis}
\end{figure*}

@@

In this multi-instrument analysis example we showcase the capabilities of
\gammapy to perform a simultaneous likelihood fit incorporating data from
different instruments and at different levels of reduction. We estimate the
spectrum of the Crab Nebula combining data from \fermi, \magic and \hawc. Maps
of \fermi data are prepared selecting a region of $X^{\circ}$ around the
position of the Crab Nebula applying the same selection criteria of the 3FHL
catalog (7 years of data with energy from $10\,{\rm GeV}$ to $2\,{\rm TeV}$,
\citealt{3FHL}).  The \magic data are two%% shall we explain exactly which type of Map is created?
observations of $20\,{\rm min}$ each, chosen from the dataset used to estimate
the performance of the upgraded stereo system \citep{magic_performance} and
already included in \cite{joint_crab}. The observations were taken at small
zenith angles ($<30^{\circ}$) in wobble mode \citep{fomin_1994}, with the
source sitting at an offset of $0.4^{\circ}$ from the FoV center. Their energy
range spans $80\,{\rm GeV} -- 20\,{\rm TeV}$. They are reduced to ON/OFF
dataset before being fitted. \hawc flux points data are estimated in
\cite{hawc_crab_2019} with $2.5\,{\rm years}$ of data and span an energy range
$300\,{\rm GeV} -- 300\,{\rm TeV}$, and directly read with \gammapy.

@@

The result of the joint fit is displayed in
Fig.~\ref{fig:multi_instrument_analysis}. We remark that the objective of this
exercise is illustrative, we display the flexibility of \gammapy in
simultaneously fitting multi-isntrument data even at different levels of
reduction, we do not aim to provide a new measurement of the Crab Nebula
spectrum.
